\titleNameLong{}

### 2015-12-07 FinalProject/Tex/paper/paper.tex
added bibliography info
fixed another word wrap issue
added challenges section

\section{Challenges of GPGPU} \label{sec:challenges}
\subsection{Heterogeneous Applications}
TODO Maximizing resource utilization while minimizing shared resource contention
between CPU and GPU is hard
\subsection{Memory Limitations}
TODO

@@

% % Bibliography
% \bibliographystyle{ACM-Reference-Format-Journals}
% \bibliography{paper-bibfile}

>>>>

\section{Challenges of GPGPU} \label{sec:challenges}
\subsection{Heterogeneous Applications}
There are two main challenges of GPGPU. The first is maintaining high
performance on heterogeneous applications. As mentioned previously, this problem
is difficult simply due to the complicated structure of these applications. When
a warp stalls for one reason or another, the warp scheduler selects a new warp
to take its place the next cycle. This is an attempt to hide the latency of warp
stalls. However, GPU schedulers are limited in their ability to hide latencies
for heterogeneous applications. This is caused by imbalanced workloads among
warps, divergent branches, irregular memory accesses, and shared cache
contention \cite{CoordinatedWarpScheduling}. Designs in the following section
discusses these issues and present possible solutions.

\subsection{Memory Limitations}
The second challenge for GPGPU is mitigating memory bandwidth bottlenecks. A
majority of general-purpose applications run on GPUs are memory bound
\cite{AssistWarps}, which means that performance is bottlenecked by off-chip
memory bandwidth. This bottleneck is commonly due to contention among warps
within the GPU, and may also be a result of contention with memory use by the
CPU in heterogeneous system architectures
\cite{ManagingConcurrencyInHeterogeneous}. A number of schemes have been
suggested to reduce pressure on off-chip memory and will be visited in the next
section.

@@

% Bibliography
\bibliographystyle{ACM-Reference-Format-Journals}
\bibliography{paper-bibfile}
